Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-02-11 manuscript/climate_sensitivity_draft.Rmd
issue #68

We identified the years with driest conditions during May-August, which stood out in the analysis of @helcoski_growing_2019 as the current-year months to which annual growth was most sensitive for trees at this site. We considered two metrics of moisture deficit: NOAA Divisional Data’s Palmer Drought Severity Index (PDSI) and the difference between monthly potential evapotranspiration (PET) and precipitation (PRE). {**ADD SPEI**} These data were obtained from the ForestGEO Climate Data Portal (https://github.com/forestgeo/Climate) in August 2018, with monthly PET and PRE sourced from Climatic Research Unit high-resolution gridded dataset (CRU TS v.4.01; @harris_updated_2014). The driest years were identified through ranking mean May-August PDSI or [PET-PRE] for the time period from driest to wettest. 
Climatically, these drought years included three of the five years between 1950 and 2009 with greatest moisture deficit (PET-PRE) during the peak growing season months of May-August (MJJA), which for this site are when annual tree growth is most sensitive [@helcoski_growing_2019]. Specifically, 1966, 1977, and 1999 had mean MJJA PET-PRE of 83, 87, and 80 mm mo<sup>-1</sup>, respectively. The years 1964 and 2007 also ranked in the top five driest (PET-PRE =84 and 82 mm mo<sup>-1</sup>), but were not among the lowest in terms of PDSI and were thus not identified as candidate years for inclusion as top drought years (Table S3).

>>>>

We identified the years with driest conditions during May-August, which stood out in the analysis of @helcoski_growing_2019 as the current-year months to which annual growth was most sensitive for trees at this site. We considered two metrics of moisture deficit: NOAA Divisional Data’s Palmer Drought Severity Index (PDSI) and the difference between monthly potential evapotranspiration (PET) and precipitation (PRE). These data were obtained from the ForestGEO Climate Data Portal (https://github.com/forestgeo/Climate) in August 2018, with monthly PET and PRE sourced from Climatic Research Unit high-resolution gridded dataset (CRU TS v.4.01; @harris_updated_2014). The driest years were identified through ranking mean May-August PDSI or [PET-PRE] for the time period from driest to wettest. 
Climatically, these drought years included three of the five years between 1950 and 2009 with greatest moisture deficit (PET-PRE) during the peak growing season months of May-August (MJJA), which for this site are when annual tree growth is most sensitive [@helcoski_growing_2019]. Specifically, 1966, 1977, and 1999 had mean MJJA PET-PRE of 83, 87, and 80 mm mo<sup>-1</sup>, respectively. The years 1964 and 2007 also ranked in the top five driest (PET-PRE =84 and 82 mm mo<sup>-1</sup>), but were not among the lowest in terms of PDSI and were thus not identified as candidate years for inclusion as top drought years (Table S3).
